%-------------------------
% Resume in Latex
% Author : Supratik Chakraborty
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Supratik Chakraborty} \\ \vspace{1pt}
    \small +91 8584832114 $|$ \href{mailto:supratikofficial1@gmail.com}{\underline{supratikofficial1@gmail.com}} $|$ 
    \href{https://supratikch.com}{\underline{supratikch.com}} $|$
    \href{https://www.linkedin.com/in/supratikch}{\underline{linkedin.com/in/supratikch}} $|$
    \href{https://github.com/deagleSC}{\underline{github.com/deagleSC}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {West Bengal University of Technology}{Jul. 2019 -- Aug. 2023}
      {B.Tech (Bachelor of Technology) in Information Technology; CGPA: 9.11}{Kolkata, India}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer (Full-Stack)}{Mar. 2024 -- Present}
      {Trumio}{Remote}
      \resumeItemListStart
        \resumeItem{Architected \textbf{multi-tenant admin backend} with \textbf{RBAC}, license enforcement, and policy-driven workflows for \textbf{5 enterprise customers (500+ users)}; reduced manual onboarding steps by \textbf{75\%} via zero-touch configuration.}
        \resumeItem{Built \textbf{authorization-aware analytics services} with strict tenant isolation for managerial reporting; cut report generation time by \textbf{90\%+} with \textbf{zero compliance violations} in production.}
        \resumeItem{Led development of \textbf{AI-powered voice interview platform} with VAPI integration, real-time transcription, and \textbf{ML-powered proctoring} using TensorFlow.js + MediaPipe; automated feedback generation and performance scoring.}
        \resumeItem{Designed \textbf{analytics ingestion layer} integrating Google Analytics and Hotjar with schema validation, rate limiting, and fault tolerance; increased trackable user events by \textbf{3x} (8 to 25+) across platform surfaces.}
        \resumeItem{Orchestrated backend pipeline processing \textbf{200--300 PRs and feedback records monthly} with PII masking and NDA boundaries; decreased weekly review time by \textbf{50\%} (6+ hours to under 3) while eliminating compliance risk.}
        \resumeItem{Owned backend delivery for \textbf{10+ production releases} with bi-weekly deployments; improved observability and rollback readiness, reducing post-release hotfixes by \textbf{50\%} (3--4 to 1--2 per cycle).}
        \resumeItem{Led \textbf{frontend performance optimization} using bundle splitting, render-path optimization, and memoization; improved Lighthouse performance scores by \textbf{26\%} (62 to 78) on key dashboard surfaces.}
        \resumeItem{Initiated \textbf{40+ component design system} distributed as npm package; optimized average component development time by \textbf{50\%} (4+ hours to under 2) for internal teams.}
        \resumeItem{\textbf{Tech Stack}: FastAPI, Python, MongoDB, REST APIs, Azure, Vite + React, Storybook, Git.}
      \resumeItemListEnd

    \resumeSubheading
      {Founding Engineer (SDE-1)}{Oct. 2023 -- Mar. 2024}
      {Reunion}{Mumbai, India}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{web scraping pipelines} using BeautifulSoup to extract structured data from \textbf{20+ government real-estate portals}; implemented \textbf{distributed ingestion workflows} with Celery + RabbitMQ processing \textbf{100+ records per run}.}
        \resumeItem{Integrated \textbf{Keycloak} for secure RBAC and maintained \textbf{scalable data pipelines} supporting real-time property data aggregation across multiple government sources.}
        \resumeItem{\textbf{Tech Stack}: Python, Celery, RabbitMQ, Keycloak, BeautifulSoup, Gatsby, Redux.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Chessvine — AI Chess Analysis Platform}}{\href{https://chessvine.vercel.app}{chessvine.vercel.app}}
          \resumeItemListStart
            \resumeItem{Architected \textbf{asynchronous AI analysis pipeline} using \textbf{Gemini 2.0 Flash} with Cloud Tasks + Cloud Run workers; generates player-specific insights and auto-creates \textbf{2 tactical puzzles per game} with median \textbf{3--4s} AI inference latency.}
            \resumeItem{Built \textbf{full-stack SaaS} featuring interactive chess board, real-time status polling, PGN bulk upload (up to 20 files), and 6 dashboard views; deployed on Cloud Run with \textbf{zero-downtime deploys} via Cloud Build CI/CD.}
            \resumeItem{\textbf{Tech Stack}: Next.js, Express, MongoDB, GCP, Docker.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Hirevine — AI-Powered Recruitment Platform}}{\href{https://hirevine.vercel.app}{hirevine.vercel.app}}
          \resumeItemListStart
            \resumeItem{Designed \textbf{serverless resume parsing system} powered by \textbf{Gemini 2.0 Flash multimodal API}; processes PDFs via Cloud Tasks + Cloud Run workers, extracting structured candidate data and computing \textbf{JD match scores} with median \textbf{6--8s} latency.}
            \resumeItem{Engineered \textbf{full-stack recruitment SaaS} featuring \textbf{real-time AI interviews} with SSE streaming, voice I/O via Web Speech API + Google Cloud TTS, and human-in-the-loop evaluation workflow.}
            \resumeItem{\textbf{Tech Stack}: Next.js, Express, PostgreSQL, GCP, Docker.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Javascript, Typescript, HTML/CSS, C++, SQL} \\
     \textbf{Frameworks \& Libraries}{: FastAPI, Node.js, Express, React, Next.js, Vite, Zustand, Redux} \\
     \textbf{Platforms \& Tools}{: Azure, Keycloak, GitHub Actions, Docker, Linux, Git, GitHub, LaTeX}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
